\documentclass{article}
\usepackage{amsmath, sfmath, pgfplots, multicol}
\pgfplotsset{compat = newest}
\usepgfplotslibrary{statistics}
\usepackage[margin = 0.5in]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\setlength\parindent{0cm}
\pagestyle{empty}

\newcounter{pset}
\newcounter{key}


\begin{document}

\subsection*{Measures of Spread P-Set}

The following are stock prices for Amazon during the last two weeks of July 2022. Round your answers to 2 decimal places.

\begin{center}
\begin{tabular}{ccccc}
    113.76 & 118.21 & 122.77 & 124.63 & 122.42 \\
    121.14 & 114.81 & 120.97 & 122.28 & 134.95 \\
\end{tabular}
\end{center}

\begin{enumerate}
    \item What is the mean of the stock prices? \label{mean}
    \item What is the range of stock prices?
    \item What is the population standard deviation?
    \item What is the population variance?
    \item What is the sample standard deviation? \label{ssd}
    \item What is the sample variance?
    \item Using your answers from questions \ref{mean} and \ref{ssd}, find the minimum and maximum ``usual" stock price values.
    \item Are there any stock prices that would be considered ``unusual"? If so, which one(s)?
    \item What is a good consequence of owning a stock with a high standard deviation?
    \item What is a bad consequence of owning a stock with a high standard deviation?
\end{enumerate}     \setcounter{pset}{\value{enumi}}

The heights of a group of professional basketball players is given. Round your answers to 1 decimal place.

\begin{center}
\begin{tabular}{c|c}
    \textbf{Height} & \textbf{Frequency} \\ \hline 
    70 -- 71 & 3 \\
    72 -- 73 & 7 \\
    74 -- 75 & 16 \\
    76 -- 77 & 12 \\
    78 -- 79 & 10 \\
    80 -- 81 & 4 \\
    82 -- 83 & 1 \\
\end{tabular}
\end{center}

\begin{enumerate}   \setcounter{enumi}{\value{pset}}
    \item Estimate the mean height of this group of basketball players.
    \item Estimate the sample standard deviation of this group of basketball players.
    \item What are the minimum and maximum ``usual" heights of these basketball players?
    \item Would any listed player's height in this group be considered ``unusual"?
\end{enumerate}

\newpage 

\texttt{Key}

\begin{enumerate}
    \item 121.59
    \item 21.19
    \item 5.56
    \item 30.96
    \item 5.86
    \item 34.40
    \item Minimum = 109.87; Maximum = 133.31
    \item 134.95
    \item Answers vary
    \item Answers vary
    \item 75.8
    \item 2.8
    \item Minimum = 70.2; Maximum = 81.4
    \item The player in the 82 -- 83 height class
\end{enumerate}

\end{document}
